Covariate analysis of MAYO reprocessed counts (with TMM normalisation)

### 2017-02-21 code/Rmd/MSSM_RNASeq_Reprocessed_TMM_BinnedCDR.Rmd
Minor modifications

# Convert factor covariates to factors
COVARIATES[,FactorCovariates] = lapply(COVARIATES[,FactorCovariates], factor)
COVARIATES[,ContCovariates] = lapply(COVARIATES[,ContCovariates], as.character)
COVARIATES[,ContCovariates] = lapply(COVARIATES[,ContCovariates], as.numeric)
```
Covariate correlation
```{r covariates.correlation, fig.width=8, fig.height=8}
COVARIATES.CORRELATION = CovariateAnalysis::getAssociationStatistics(COVARIATES, PVAL = 0.05)
ggheatmap.show(COVARIATES.CORRELATION$plot, col.width=0.4, row.width=0.1)
```
### Gene Filtering
Preprocess counts matrix and metadata. Determine design matrix for normalisation and differential expression analysis.

>>>>

# Convert factor covariates to factors
COVARIATES[,FactorCovariates] = lapply(COVARIATES[,FactorCovariates], factor)
COVARIATES[,ContCovariates] = lapply(COVARIATES[,ContCovariates], as.character)
COVARIATES[,ContCovariates] = lapply(COVARIATES[,ContCovariates], as.numeric)
```
Covariate correlation
```{r covariates.correlation, fig.width=8, fig.height=8}
COVARIATES.CORRELATION = CovariateAnalysis::getAssociationStatistics(COVARIATES, PVAL = 0.05)
COVARIATES.CORRELATION$plot
```
### Gene Filtering
Preprocess counts matrix and metadata. Determine design matrix for normalisation and differential expression analysis.

### 2017-02-21 code/Rmd/Mayo_RNASeq_Reprocessed_TMM.Rmd
Minor modifications

plotdata.cer = plotdata[grep('CER', plotdata$ID),]
p <- ggplot(plotdata.cer, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape=factor(Source), color=as.factor(Tissue), size=as.numeric(AgeAtDeath)))
p <- p + theme_bw() + theme(legend.position="right") +scale_shape_manual(values = 1:2)
# p <- p + geom_text(aes(label= ID), size=4, hjust=0)
pl[[1]] <- p

plotdata.tcx = plotdata[grep('TCX', plotdata$ID),]
p <- ggplot(plotdata.tcx, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape=factor(Source), color=as.factor(Tissue), size=as.numeric(AgeAtDeath)))
p <- p + theme_bw() + theme(legend.position="right") +scale_shape_manual(values = 1:2)
# p <- p + geom_text(aes(label= ID), size=4, hjust=0)
pl[[2]] <- p

multiplot(plotlist = pl, cols = 1)
```
```{r decompse.normalise.data2, fig.height=9, fig.width=25, results='asis'}
# Tree based clustering
sampleTrees = flashClust::hclust(dist(t(VOOM.GENE_EXPRESSION$E)), method = "average")
tree = WGCNA::cutreeStatic(sampleTrees, cutHeight = 135, minSize=10)

>>>>

plotdata[grep('CER', plotdata$ID),'Region'] = 'CER'
plotdata[grep('TCX', plotdata$ID),'Region'] = 'TCX'
plotdata$Region = factor(plotdata$Region)
plotdata$Source = factor(plotdata$Source)

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape = Source, color = Region))
p <- p + theme_bw() + theme(legend.position = "left") +scale_shape_manual(values = 1:2)
p <- p + facet_grid(Region~.)
# p <- p + geom_text(aes(label= ID), size=4, hjust=0)
p
```
```{r decompse.normalise.data2, fig.height=9, fig.width=25, results='asis'}
# Tree based clustering
sampleTrees = flashClust::hclust(dist(t(VOOM.GENE_EXPRESSION$E)), method = "average")
tree = WGCNA::cutreeStatic(sampleTrees, cutHeight = 135, minSize=10)
